|

### 2023-02-06 paper.Rmd
autogit

# Abstract

...

@@

# Nomenclature {.unnumbered #I}

## Symbols {.unnumbered #I}

```{r Symbols, echo=FALSE, message=FALSE, warning=FALSE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/nomenclature.csv", sep = "?"),
  caption = "List of Mathematical Symbols",
  format = "markdown"
)%>% row_spec(0,bold=TRUE )
```
## Abbreviations {.unnumbered #II}

@@

# References {.unnumbered #II}

>>>>

# Abstract {.unnumbered #I}
...

@@

# Nomenclature {.unnumbered #II}

## Symbols {.unnumbered #IIa}

```{r Symbols, echo=FALSE, message=FALSE, warning=FALSE}
fig.pos="H"
knitr::kable(
  read.csv("./tables/nomenclature.csv", sep = "?"),
  caption = "List of Mathematical Symbols",
  format = "markdown"
)%>% row_spec(0,bold=TRUE )
```
## Abbreviations {.unnumbered #IIb}

@@

# References {.unnumbered #III}
